Verifying Demonstrations

### 2021-06-17 paper/verifiability-analysis.tex

Relaying the communication is an attack against the \ac{DB} protocol.
We assumed \iac{DB} protocol with \ac{DBTF} resistance (the most relevant 
property for this situation), so Alice cannot succeed with more than negligible 
probability.
(\Ac{DBDF} is captured by \ac{DBTF} in this case, as in \ac{DBTF} she has a 
colluder.
\Ac{DBMF} would prevent Alice from relaying unsuspecting bystanders' 
communication to witnesses.
\ac{DBDH} is not really useful to Alice in this situation.)

>>>>

Relaying the communication is an attack against the \ac{DB} protocol.
Due to the construction of \textcite{DB-Schnorr}, Alice cannot succeed with 
more than negligible probability.
